|

### 2021-03-13 supplementary_information_sciad.Rmd
Update supplementary_information_sciad.Rmd

For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes. The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007]. Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method is applicable to models with variable transformations and allows direct comparisons of the effect sizes of watershed area and branching probability (see **Supplementary Text** for further details). We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].

@@

For regression models, standardized regression coefficients (or its variant) are perhaps the most common summary when comparing effect sizes of explanatory variables. These values are useful if they are directly interpretable. For example, in linear regression models without interactions and variable transformations, regression coefficients have direct interpretations as they represent additive effects. However, there are many cases where regression coefficients are difficult to interpret. In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations at the original scale of the response variable $y$ (i.e., species richness).

>>>>

For the supported model of $\gamma$ diversity, we estimated average predictive comparisons of watershed area and branching probability to compare their effect sizes. The average predictive comparison is an expected change of the response variable per a unit difference of the explanatory variable of interest [@gelmanAveragePredictiveComparisons2007]. Unlike other common metrics of effect size (e.g., standardized regression coefficients), this method provides intuitive yet rigorous estimates of effect size in models with non-linear variable transformations (see **Supplementary Text** for further details). We performed statistical analysis using R version 4.0.2 [@rcoreteamLanguageEnvironmentStatistical2020].

@@

For regression models, standardized regression coefficients (or its variant) are perhaps the most common summary when comparing effect sizes of explanatory variables. These values are useful if they are directly interpretable. For example, in linear regression models without interactions and variable transformations, regression coefficients have direct interpretations as they represent additive effects. However, there are many cases where regression coefficients are difficult to interpret. In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations on the original scale of the response variable $y$ (i.e., species richness).
